---
title: "Legionnaires’ disease in Europe: increasing trend in 2017-2019"
output: 
  flexdashboard::flex_dashboard:
runtime: shiny
editor_options:
  chunk_output_type: console
---

<style>                     
.navbar {
  background-color:#65B32E;
  border-color:#207732;
}
.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
  color:white;
  background-color:#207732;
}
.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: white;
  background-color:#207732;
}


</style>  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

##################### Settings ##################
# profvis::profvis(expr=rmarkdown::run("C:/R/legi_analysis/legi_analysis/legi_analysis.Rmd"),
#                  prof_output="C:/R/legi_analysis/legi_analysis/legi_analysis.html")

## load packages
library(tidyverse)
library(fpp3)
library(knitr)
library(kableExtra)
library(DT)
library(plotly)
library(forecast)
library(janitor)
library(flexdashboard)
library(shiny)
library(gridExtra)

## open functions
source("legi_functions.R")

######################### prepare the data ############################

legi_tsibble <- read_rds("legi_tsibble.rds")

## create vectors of stratifications
imported <- as.factor(unique(legi_tsibble$Imported3)[!is.na(unique(legi_tsibble$Imported3))])
agearoups <- as.factor(unique(legi_tsibble$AgeGroup2)[!is.na(unique(legi_tsibble$AgeGroup2)) &
                                                       unique(legi_tsibble$AgeGroup2)!="Unknown"])
genders <- unique(legi_tsibble$Gender)[!is.na(unique(legi_tsibble$Gender)) &
                                         unique(legi_tsibble$Gender)!="UNK"]
```

Overview 2012-2019
==================

Sidebar {.sidebar}
---------------------

#### **Abstract**

**Background:**
Burden of Legionnaires’ disease (LD) in EU/EEA has increased under the last decade, with annual notification rates increasing from 1.2-1.4 per 100,000 under 2012-2016, to 1.8-2.2 within 2017-2019.

**Aim:**
We aimed to measure the amount of weekly excess cases under the period 2017-2019 based on previous year trends and whether there was a significant change in trend during this period. Moreover, we aimed to assess if there were differences according to age, gender, or level of imported infections. 

**Methods:**
We collated 2012-2019 annual surveillance data from the European Surveillance System (TESSy) reported by EU/EEA countries. A retrospective prediction by dynamic regression model was created from 2012-2016 data to analyse the percentage increase in cases in 2017-2019. Interrupted time series (ITS) analysis was also performed to determine if there had been a significant change in trend in 2017-2019 compared with the previous five years.

**Results:** 
Overall, we found a 33.4% increase in cases in 2017-2019 compared with predicted. The ITS also found a significant trend increase in 2017-2019 compared with 2012-2016. A significant trend increase was observed mostly among older age groups, males, and domestic cases.

**Conclusion:**
Our study showed a significant increasing trend in LD cases in the EU/EEA during 2017-2019 compared with the previous five years. The distribution of cases per week suggests an overall amplification of the seasonal trends. These findings support that LD continues to be an infectious disease of public health concern in the EU/EEA, warranting further research into determinants of the increase.


Time series {.tabset}
------------------
### Time series
```{r time series, results="asis"}
europe <- legi_tsibble |> 
  summarise(cases=sum(nb))

## create plot
p <- ggplot() +
    geom_line(europe, 
              mapping=aes(x=as.Date(week), y=cases, colour="LD cases"), size=1) +
    scale_x_date(date_labels = "  %Y", date_breaks= "1 year", expand = c(0, 0),
                 limits=c(as.Date("2012-01-01"),as.Date("2020-01-01"))) + 
    scale_y_continuous(expand = c(0, 0)) +
    coord_cartesian(ylim=c(0, NA)) +
    ylab("Cases") + xlab("Year") +
    scale_colour_manual("lines", values=c("LD cases" = rgb(101,179,46,maxColorValue = 255))) +
    theme(axis.text=element_text(size=10),
          axis.title=element_text(size=12)) +    #Axis text style
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.background = element_blank()) +  #Empty backgroud
    theme(axis.line = element_line(colour = "#767171") ) +
    theme(legend.position = "right", legend.title =element_blank(), 
          legend.text =element_text(size=12), plot.title = element_text(size=12),
          legend.key=element_blank(), legend.key.width = unit(0.8, "cm")) +
    guides(fill=guide_legend(reverse=TRUE), colour=guide_legend(reverse=TRUE)) +
  ggtitle("Weekly LD cases by date of onset, EU/EEA, 2012-2019")
ggplotly(p) |> 
      layout(legend=list(title=list(text=" ")))
```


### Heat map
```{r heatmap,results="asis"}
europe_heat <- legi_tsibble |> summarise(Cases=sum(nb)) |> as_tibble() |>  
  mutate(year=year(week), year=as.character(year), year=reorder(year, desc(year)),
         week=as.character(week), week=substring(week,7), week=as.numeric(week))

p <- europe_heat |> ggplot(aes(week, year, fill=Cases)) +
  geom_tile(colour="white") + 
  scale_x_continuous(breaks=c(1,13,26,38,50), expand = c(0, 0)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank()) +
  theme(axis.text=element_text(size=10), plot.title = element_text(size=12),
          axis.title=element_text(size=12)) +    #Axis text style
  scale_fill_gradient2(low=rgb(241, 214, 118,maxColorValue = 255), 
                       mid=rgb(204, 107, 33,maxColorValue = 255),
                       high=rgb(124, 23, 15,maxColorValue = 255), 
                       na.value="transparent", midpoint=250) +
  xlab("Week") + ylab("Year") + ggtitle("Weekly LD cases by date of onset, EU/EEA, 2012-2019")
ggplotly(p)
```

2017-2019 retrospective prediction
==================

Sidebar {.sidebar}
---------------------
```{r sidebar_prediction}
selectInput("select_prediction",label="Select group",
            choices=c("All","Imported","Not imported","<40","40-49","50-59","60-69",
                      "70-79","80>=","F","M"))
```

Retrospective prediction {.tabset}
---------------------
### Plot results
```{r europe tsibble, results="asis"}
renderPlotly({
  
  if(input$select_prediction=="All"){
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_all.rds"),
               legi_tsibble |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="Imported") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_imported.rds"),
               legi_tsibble |> filter(Imported3=="Imported") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="Not imported") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_notimported.rds"),
               legi_tsibble |> filter(Imported3=="Not imported") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="<40") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_40.rds"),
               legi_tsibble |> filter(AgeGroup2=="<40") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="40-49") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_40_49.rds"),
               legi_tsibble |> filter(AgeGroup2=="40-49") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="50-59") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_50_59.rds"),
               legi_tsibble |> filter(AgeGroup2=="50-59") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="60-69") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_60_69.rds"),
               legi_tsibble |> filter(AgeGroup2=="60-69") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="70-79") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_70_79.rds"),
               legi_tsibble |> filter(AgeGroup2=="70-79") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="80>=") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_80.rds"),
               legi_tsibble |> filter(AgeGroup2=="80>=") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_prediction=="F") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_female.rds"),
               legi_tsibble |> filter(Gender=="F") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
    
  }
   else if(input$select_prediction=="M") {
    ggplotly(shiny_plot(readRDS("Models and plots/forecast_male.rds"),
               legi_tsibble |> filter(Gender=="M") |> summarise(cases=sum(nb)))) |> 
      layout(legend=list(title=list(text=" ")))
  }
})
```

### Table results
```{r retrospective table,results='asis'}
renderUI({
  
  if(input$select_prediction=="All"){
    shiny_excess(readRDS("Models and plots/forecast_all.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="Imported") {
    shiny_excess(readRDS("Models and plots/forecast_imported.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="Not imported") {
    shiny_excess(readRDS("Models and plots/forecast_notimported.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="<40") {
    shiny_excess(readRDS("Models and plots/forecast_40.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="40-49") {
    shiny_excess(readRDS("Models and plots/forecast_40_49.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="50-59") {
    shiny_excess(readRDS("Models and plots/forecast_50_59.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="60-69") {
    shiny_excess(readRDS("Models and plots/forecast_60_69.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="70-79") {
    shiny_excess(readRDS("Models and plots/forecast_70_79.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="80>=") {
    shiny_excess(readRDS("Models and plots/forecast_80.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="F") {
    shiny_excess(readRDS("Models and plots/forecast_female.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  } else if(input$select_prediction=="M") {
    shiny_excess(readRDS("Models and plots/forecast_male.rds"))
    HTML(rbind(table_2017, table_2018, table_2019, total_table) |> 
    knitr::kable(digits=c(0,0,0,0,0,1,0,1), "html", align="c",
          col.names=c(" ", "Observed cases (O)", "Expected cases (E)", "Cases upper 95% PI", 
                      "O-E", "Percent change (%)", "Number", "Percent change (%)")) |>
    kable_styling(bootstrap_options = c("striped", "hover")) |>
    add_header_above(c(" "=4, "Cases above prediction"=2, "Cases above 95% PI"=2)) |>
    column_spec(2:8, width=2) |> column_spec(1,bold=TRUE))
    
  }
})

```

### Model
```{r prediction model,results='asis'}
renderUI({
  if(input$select_prediction=="All"){
    HTML(readRDS("Models and plots/model_all.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_all.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))

  } else if(input$select_prediction=="Imported"){
    HTML(readRDS("Models and plots/model_imported.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_imported.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="Not imported"){
    HTML(readRDS("Models and plots/model_notimported.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_notimported.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="<40"){
    HTML(readRDS("Models and plots/model_40.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_40.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="40-49"){
    HTML(readRDS("Models and plots/model_40_49.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_40_49.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="50-59"){
    HTML(readRDS("Models and plots/model_50_59.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_50_59.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="60-69"){
    HTML(readRDS("Models and plots/model_60_69.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_60_69.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="70-79"){
    HTML(readRDS("Models and plots/model_70_79.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_70_79.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="80>="){
    HTML(readRDS("Models and plots/model_80.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_80.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="F"){
    HTML(readRDS("Models and plots/model_female.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_female.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
    
  } else if(input$select_prediction=="M"){
    HTML(readRDS("Models and plots/model_male.rds") |>
      coef() |> select(-.model) |>
    kable(col.names=c("Term", "Estimate", "Standard error", "Test statistic", "P-value"),
          digits=3,caption=print(augment(readRDS("Models and plots/model_male.rds"))[1,1])) |>
    kable_styling(bootstrap_options = c("striped", "condensed","hover")))
  }
})
```

### Residuals
```{r rprediction residuals,results='asis'}
renderPlot({
  if(input$select_prediction=="All"){
    readRDS("Models and plots/model_all.rds") |>  
      gg_tsresiduals(lag_max=52)

  } else if(input$select_prediction=="Imported"){
    readRDS("Models and plots/model_imported.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="Not imported"){
    readRDS("Models and plots/model_notimported.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="<40"){
    readRDS("Models and plots/model_40.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="40-49"){
    readRDS("Models and plots/model_40_49.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="50-59"){
    readRDS("Models and plots/model_50_59.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="60-69"){
    readRDS("Models and plots/model_60_69.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="70-79"){
    readRDS("Models and plots/model_70_79.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="80>="){
    readRDS("Models and plots/model_80.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="F"){
    readRDS("Models and plots/model_female.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_prediction=="M"){
    readRDS("Models and plots/model_male.rds") |>  
      gg_tsresiduals(lag_max=52)
  }
})
```


2017 interrupted time series
==================

Sidebar {.sidebar}
---------------------
```{r sidebar_its}
selectInput("select_its",label="Select group",
            choices=c("All","Imported","Not imported","<40","40-49","50-59","60-69",
                      "70-79","80>=","F","M"))
```

Interrupted time series {.tabset}
-----------------------
### Results
```{r its analysis,results="asis"}
renderPlotly({
  
  if(input$select_its=="All"){
    ggplotly(readRDS("Models and plots/itsplot_all.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="Imported") {
    ggplotly(readRDS("Models and plots/itsplot_imported.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="Not imported") {
    ggplotly(readRDS("Models and plots/itsplot_notimported.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="<40") {
    ggplotly(readRDS("Models and plots/itsplot_40.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="40-49") {
    ggplotly(readRDS("Models and plots/itsplot_40.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="50-59") {
    ggplotly(readRDS("Models and plots/itsplot_50_59.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="60-69") {
    ggplotly(readRDS("Models and plots/itsplot_60_69.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="70-79") {
    ggplotly(readRDS("Models and plots/itsplot_70_79.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="80>=") {
    ggplotly(readRDS("Models and plots/itsplot_80.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="F") {
    ggplotly(readRDS("Models and plots/itsplot_female.rds")) |> 
      layout(legend=list(title=list(text=" ")))
    
  } else if(input$select_its=="M") {
    ggplotly(readRDS("Models and plots/itsplot_male.rds")) |> 
      layout(legend=list(title=list(text=" ")))
  }
})
```

### Model
```{r its model,results='asis'}
renderUI({
  if(input$select_its=="All"){
    HTML(readRDS("Models and plots/itsmodel_all.rds"))

  } else if(input$select_its=="Imported"){
    HTML(readRDS("Models and plots/itsmodel_imported.rds"))
    
  } else if(input$select_its=="Not imported"){
    HTML(readRDS("Models and plots/itsmodel_notimported.rds"))
    
  } else if(input$select_its=="<40"){
    HTML(readRDS("Models and plots/itsmodel_40.rds"))
    
  } else if(input$select_its=="40-49"){
    HTML(readRDS("Models and plots/itsmodel_40_49.rds"))
    
  } else if(input$select_its=="50-59"){
    HTML(readRDS("Models and plots/itsmodel_50_59.rds"))
    
  } else if(input$select_its=="60-69"){
    HTML(readRDS("Models and plots/itsmodel_60_69.rds"))
    
  } else if(input$select_its=="70-79"){
    HTML(readRDS("Models and plots/itsmodel_70_79.rds"))
    
  } else if(input$select_its=="80>="){
    HTML(readRDS("Models and plots/itsmodel_80.rds"))
    
  } else if(input$select_its=="F"){
    HTML(readRDS("Models and plots/itsmodel_female.rds"))
    
  } else if(input$select_its=="M"){
    HTML(readRDS("Models and plots/itsmodel_male.rds"))
  }
})
```


### Residuals
```{r its residuals,results="asis"}
renderPlot({
  if(input$select_its=="All"){
    readRDS("Models and plots/its_model_all.rds") |>  
      gg_tsresiduals(lag_max=52)

  } else if(input$select_its=="Imported"){
    readRDS("Models and plots/its_model_imported.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="Not imported"){
    readRDS("Models and plots/its_model_notimported.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="<40"){
    readRDS("Models and plots/its_model_40.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="40-49"){
    readRDS("Models and plots/its_model_40_49.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="50-59"){
    readRDS("Models and plots/its_model_50_59.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="60-69"){
    readRDS("Models and plots/its_model_60_69.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="70-79"){
    readRDS("Models and plots/its_model_70_79.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="80>="){
    readRDS("Models and plots/its_model_80.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="F"){
    readRDS("Models and plots/its_model_female.rds") |>  
      gg_tsresiduals(lag_max=52)
    
  } else if(input$select_its=="M"){
    readRDS("Models and plots/its_model_male.rds") |>  
      gg_tsresiduals(lag_max=52)
  }
})
```